Discrete Ordinates

### 2016-04-08 docprep/draft1.tex
Updated the code in docprep

\begin{lstlisting}[escapeinside={(*}{*)}]
  (*$\Psi(x, y, z, E, \hat{\Omega}) \leftarrow 123$*)
  list= { (*$S_1,S_2,S_3$*) }
\end{lstlisting}

\begin{lstlisting}[escapeinside={(*}{*)}]
for (*$E \in \mathcal{E}$*) in descending order
  for (*$\Omega \in Q$*) in any order
    if (*$\mu(\Omega) > 0$*) and (*$\xi(\Omega) > 0$*) and (*$\eta(\Omega) > 0$*)
      for (*$x \in X$*) in ascending order
        for (*$y \in Y$*) in ascending order
          for (*$z \in Z$*) in ascending order
            (*$\Psi_{x-in}(x, y, z, E, \Omega) \leftarrow 123$*)
            (*$\Psi_{y-in}(x, y, z, E, \Omega) \leftarrow 123$*)
            (*$\Psi_{z-in}(x, y, z, E, \Omega) \leftarrow 123$*)
            (*$\Psi(x, y, z, E, \Omega) \leftarrow 123$*)

            (*$\Phi(x, y, z, E) \leftarrow \Phi(x, y, z, E) + \omega(\Omega) \Psi(x, y, z, E, \Omega)$*)
  list= { (*$S_1,S_2,S_3$*) }
\end{lstlisting}

>>>>

Given:
\begin{itemize}
\item A list of all energies, $\mathcal{E}$
\item A list of all directions in the quadrature, $Q$
\item A mapping from $r$ to zone number, $\mathcal{Z}(r)$
\item Lists of direction cosines, $\mu$, $\xi$, and $\eta$
\item A map of $r$ to voxel volume, $V(r)$
\item A list of all $x$, $y$, and $z$ voxel centers, $X$, $Y$, and $Z$
\item A list of weights for the quadrature, $\omega$
\item A list of scatter cross sections in zone $\mathcal{Z}(r)$ from energy $E'$ to $E$, $\Sigma_s(\mathcal{Z}(r), E', E)$
\item A list of total cross sections in zone $\mathcal{Z}(r)$ at energy $E$, $\Sigma_T(\mathcal{Z}(r), E)$
\item The surface area of all voxels, $A_{xy}(r)$, $A_{yz}(r)$, $A_{xz}(r)$
\end{itemize}

\pagebreak
\begin{lstlisting}[escapeinside={(*}{*)}]
function sweep()

  (*$\phi(r, E) = \vec{0}$*)    # Scalar flux
  (*$\Psi(r, \Omega, E) = \vec{0}$*)  # Angular flux

  for (*$E \in \mathcal{E}$*) in descending order
    while not converged
      for (*$\Omega \in Q$*) in any order
        if (*$\mu(\Omega) > 0$*) and (*$\xi(\Omega) > 0$*) and (*$\eta(\Omega) > 0$*)
          octant1()
        else if (*$\mu(\Omega) > 0$*) and (*$\xi(\Omega) > 0$*) and (*$\eta(\Omega) < 0$*)
          octant2()
        ...
        else
          octant8()
\end{lstlisting}

\pagebreak
\begin{lstlisting}[escapeinside={(*}{*)}]
function octant1()

  for (*$x \in X$*) in ascending order
    for (*$y \in Y$*) in ascending order
      for (*$z \in Z$*) in ascending order

        (*$S$*) = totalScatter((*$x, y, z, \Omega, E$*))

        # Get the in-flux from the previous out-flux
        (*$\Psi_{x-in}(x, y, z, E, \Omega) \leftarrow \Psi_{x-out}(x-\Delta x, y, z, E, \Omega)$*)
        (*$\Psi_{y-in}(x, y, z, E, \Omega) \leftarrow \Psi_{x-out}(x, y-\Delta y, z, E, \Omega)$*)
        (*$\Psi_{z-in}(x, y, z, E, \Omega) \leftarrow \Psi_{x-out}(x, y, z-\Delta z, E, \Omega)$*)

        # Calculate the angular flux
        (*$n \leftarrow S + 2\mu(\Omega)A_{yz}(y,z)\Psi_{x-in}(x,y,z,E,\Omega) + $*)
               (*$2\xi(\Omega)A_{xz}(x,z)\Psi_{y-in}(x,y,z,E,\Omega) + $*)
               (*$2\eta(\Omega)A_{xy}(x,y)\Psi_{z-in}(x,y,z,E,\Omega)$*)
        (*$d \leftarrow 2\mu(\Omega)A_{yz}(y,z) + 2\xi(\Omega)A_{xz}(x,z) + 2\eta(\Omega)A_{xy}(x,y) + \Sigma_T(\mathcal{Z}(r), E)$*)
        (*$\Psi(x, y, z, E, \Omega) \leftarrow n/d $*)

        # Calculate the out-flux
        (*$\Psi_{x-out}(x, y, z, E, \Omega) \leftarrow 2 \Psi(x, y, z, E, \Omega) - \Psi_{x-in}(x, y, z, E, \Omega)$*)
        (*$\Psi_{y-out}(x, y, z, E, \Omega) \leftarrow 2 \Psi(x, y, z, E, \Omega) - \Psi_{y-in}(x, y, z, E, \Omega)$*)
        (*$\Psi_{z-out}(x, y, z, E, \Omega) \leftarrow 2 \Psi(x, y, z, E, \Omega) - \Psi_{z-in}(x, y, z, E, \Omega)$*)

        # Increment the scalar flux
        (*$\phi(x, y, z, E) \leftarrow \phi(x, y, z, E) + \omega(\Omega) \Psi(x, y, z, E, \Omega)$*)
\end{lstlisting}

\pagebreak
\begin{lstlisting}[escapeinside={(*}{*)}]
function totalScatter((*$r, \Omega, E$*))

  # Assume a point source at (*\color{mygreen} $r_0$*) with energy (*\color{mygreen} $E_0$*) and strength (*\color{mygreen} $S_0$*) particles / sec
  (*$S_x \leftarrow 0$*)
  if (*$r = r_0$*) and (*$E = E_0$*)
    (*$S_x \leftarrow (1/4\pi) \times S_0$*)

  (*$S_D \leftarrow 0$*)
  for (*$E' \in \mathcal{E} | E' \geq E$*)
    (*$S_D = S_D + (1/4\pi) \times \phi(r, \Omega, E') \times \Sigma_s(\mathcal{Z}(r), E', E) \times V(r)$*)

  (*$S_T = S_x + S_D$*)
  return (*$S_T$*)
\end{lstlisting}
